Drug sensitivity prediction with the normal inverse Gaussian prior informed by external data

### 2019-11-28 docs/manuscript1.Rnw
added lpml calculations to analysis_gdsc.R

	\subsection{Results}
<<simulation_gdsc_res1>>=
res <- read.table("results/simulations_gdsc_res1.txt", row.names=NULL)
temp <- res[, 1]
res <- as.matrix(res[, -1])
rownames(res) <- temp
true.phi <- mean(1/(c(1, 1, 3, 7) %*% t(unname(model.matrix(~ factor(1:4))))))
est.phi <- median(1/res[rownames(res)=="alphaf0", 1])
est.lambdaf <- apply(res[rownames(res)=="lambdaf", c(1, 2)], 2, median)
tab <- cbind(apply(res[rownames(res)=="emse", ], 2, median),
             apply(res[rownames(res)=="pmse", ], 2, median))
tab <- round(tab, 3)
tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1] <- 
  paste0("\\textbf{", tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1], "}")
tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2] <- 
  paste0("\\textbf{", tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2], "}")
colnames(tab) <- c("$\\text{EMSE}_{\\text{test}}$",
                   "$\\text{PMSE}_{\\text{test}}$")     
@	
  Figure \ref{fig:simulations_gdsc_est1} shows the estimated
	$\bm{\alpha}_{\text{feat}}$ together with its true value for NIG$_{\text{f}}$ 
	in version 1 of the simulation study. Figure 
	\ref{fig:simulations_gdsc_est1}a shows that 
	$\bm{\alpha}_{\text{feat}}$ is slightly but 
	consistently underestimated. On the $\phi_{jd}$ scale this underestimation is
	almost undetectable as depicted in Figure
	\ref{fig:simulations_gdsc_est1}b. $\lambda_{\text{feat}}$ is slightly 
	overestimated with median estimate \Sexpr{round(est.lambdaf[2], 2)} (the
	true value is 1). The overestimated $\lambda_{\text{feat}}$ translates 
	into underestimated $\gamma_{jd}^2$ variances. Underestimation of variances is 
	a common phenomenon in variational Bayes approximations. In addition, 
	$\lambda_{\text{feat}}$ is a higher level scale
	parameter, which are, in general, hard to estimate. 
<<simulations_gdsc_est1, fig.cap="Estimated (a) hyperparameters $\\bm{\\alpha}_{\\text{feat}}$ and (b) prior means $\\bm{\\phi}_{jd}$ from simulation version 1 with fixed $\\tau_d^2$.", out.width="100%", fig.asp=1/2>>= 
@

@@

	Table \ref{tab:simulations_gdsc_tab1} displays median estimation MSE (EMSE) 
	and prediction MSE (PMSE) for simulation version 1. The table includes as a
	reference the null model, which
	is an empty model that only fits the means of the $\y_{d}$.
	Estimation MSE (EMSE) and prediction MSE (PMSE) give measures of predictive 
	performance. Focussing on MSE, we see that the NIG$_{\text{f}}$ model, 
	that includes the external covariates, performs best, both in terms of 
	estimation and prediction. The lower MSEs confirm that the model that
	includes the external data (NIG$_{\text{f}}$) learns the underlying structure 
	in the data better than model NIG$_{\text{f}}^-$ that does not include the
	external data.
<<simulations_gdsc_tab1>>=
library(knitr, quietly=TRUE, verbose=FALSE)
suppressWarnings(library(kableExtra))
options(knitr.kable.NA="", digits=3)
kable(tab, col.names=colnames(tab), align="r",
      caption="Median performance measure estimates for simulation version 1 (lowest in bold).", 
      format="latex", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(latex_options=c("HOLD_position"))
@

<<simulation_gdsc_res2>>=
res <- read.table("results/simulations_gdsc_res2.txt", row.names=NULL)
temp <- res[, 1]
res <- as.matrix(res[, -1])
rownames(res) <- temp
true.chi <- mean(1/(c(1, 1, 3, 7) %*% t(unname(model.matrix(~ factor(1:4))))))
est.chi <- median(1/res[rownames(res)=="alphad0", 1])
est.lambdad <- apply(res[rownames(res)=="lambdad", c(1, 2)], 2, median)
tab <- cbind(apply(res[rownames(res)=="emse", ], 2, median),
             apply(res[rownames(res)=="pmse", ], 2, median))
tab <- round(tab, 3)
tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1] <- 
  paste0("\\textbf{", tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1], "}")
tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2] <- 
  paste0("\\textbf{", tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2], "}")
colnames(tab) <- c("$\\text{EMSE}_{\\text{test}}$",
                   "$\\text{PMSE}_{\\text{test}}$")     
@	
  Figure \ref{fig:simulations_gdsc_est2} shows the estimated
	$\bm{\alpha}_{\text{drug}}$ together with its true value for NIG$_{\text{d}}$ 
	in version 2 of the simulation study. They are estimated without bias.
	Median $\lambda_{\text{drug}}=\Sexpr{round(est.lambdad[2], 2)}$ is slightly 
	overestimated compared to true value 1. 
	The median $\chi$ estimate in the NIG$_{\text{d}}^-$ model is 
	\Sexpr{round(est.chi, 2)},  
	which is almost equal to the true mean \Sexpr{round(true.chi, 2)}. 
	$\lambda_{\text{drug}}$ is underestimated with median estimate
	\Sexpr{round(est.lambdad[1], 2)} compared to the true value.
	Median performance measures for simulation version 2 are displayed in Table
	\ref{tab:simulations_gdsc_tab2}. Again, we see that NIG$_{\text{d}}$ performs
	best in terms of MSE. However, NIG$_{\text{d}}^-$ performance is the same 
	here, indicating that the external covariates do not add much here.
<<simulations_gdsc_est2, fig.cap="Estimated (a) hyperparameters $\\bm{\\alpha}_{\\text{feat}}$ and (b) prior means $\\bm{\\phi}_{jd}$ from simulation version 2 with fixed $\\gamma_{jd}^2$.", out.width="100%", fig.asp=1/2>>= 
@

<<simulations_gdsc_tab2>>=
library(knitr, quietly=TRUE, verbose=FALSE)
suppressWarnings(library(kableExtra))
options(knitr.kable.NA="", digits=3)
kable(tab, col.names=colnames(tab), align="r",
      caption="Median performance measure estimates for simulation version 2 (best performing model in bold).", 
      format="latex", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(latex_options=c("HOLD_position"))
@

@@

phi.ratio <- apply(apply(sapply(0:3, function(s) {
  res[rownames(res)==paste0("alphaf" ,s), colnames(res)=="NIG2"]}) %*% 
    t(cbind(1, rbind(0, diag(3)))), 2, function(m) {
      res[rownames(res)=="alphaf0", colnames(res)=="NIG2"]/m}), 2, median)
chi.ratio <- apply(apply(sapply(0:3, function(s) {
  res[rownames(res)==paste0("alphad" ,s), colnames(res)=="NIG2"]}) %*% 
    t(cbind(1, rbind(0, diag(3)))), 2, function(m) {
      res[rownames(res)=="alphad0", colnames(res)=="NIG2"]/m}), 2, median)
true.ratio <- as.numeric(1/(c(1, 1, 3, 7) %*% 
                              t(unname(model.matrix(~ factor(1:4))))))

tab <- cbind(apply(res[rownames(res)=="emse", ], 2, median),
             apply(res[rownames(res)=="pmse", ], 2, median))
tab <- round(tab, 3)
tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1] <- 
  paste0("\\textbf{", tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1], "}")
tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2] <- 
  paste0("\\textbf{", tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2], "}")
colnames(tab) <- c("$\\text{EMSE}_{\\text{test}}$",
                   "$\\text{PMSE}_{\\text{test}}$")     
@	
  In Figure \ref{fig:simulations_gdsc_est3} the 
	$\bm{\alpha}_{\text{feat}}$ and $\bm{\alpha}_{\text{drug}}$ estimated by 
	NIG$_{\text{f}+\text{d}}$
	are displayed together with their true values for
	simulation 3. $\bm{\alpha}_{\text{feat}}$ are underestimated, while 
	$\bm{\alpha}_{\text{drug}}$ are overestimated. These biases seem to 
	be consistent though. The median ratios $\phi_1$ to $\phi_2$, $\phi_3$, 
	$\phi_4$ and $\chi_1$ to $\chi_2$, $\chi_3$, 
	$\chi_4$ are \Sexpr{round(phi.ratio, 2)[-1]} and 
	\Sexpr{round(chi.ratio, 2)[-1]}, respectively, compared to their true values
	\Sexpr{round(true.ratio, 2)[-1]}. So in a relative sense, the estimates are
	correct. Median $\lambda_{\text{feat}}$ and $\lambda_{\text{drug}}$ are
	are over- and underestimated with \Sexpr{round(est.lambdaf[2], 2)}
	and \Sexpr{round(est.lambdad[2], 2)}, respectively, compared to their true
	value 1. The NIG$_{\text{f}+\text{d}}^-$ model is also consistently over- 
	and underestimating $\phi$
	and $\chi$ with estimates \Sexpr{round(est.phi, 2)} and 
	\Sexpr{round(est.chi, 2)}, respectively (compared to the true mean 
	\Sexpr{round(true.chi, 2)}). NIG$_{\text{f}+\text{d}}^-$ also over- and
	underestimates 
	$\lambda_{\text{feat}}$ and $\lambda_{\text{drug}}$ with median estimates
	\Sexpr{round(est.lambdaf[1], 2)}
	and \Sexpr{round(est.lambdad[1], 2)}, respectively. Table 
	\ref{tab:simulations_gdsc_tab3}, with median performance measures, shows
	that NIG$_{\text{f}+\text{d}}$ outperforms the other models in terms of
	prediction and estimation MSE.
<<simulations_gdsc_est3, fig.cap="Estimated (a) hyperparameters $\\bm{\\alpha}_{\\text{feat}}$ and (b) prior means $\\bm{\\phi}_{jd}$ from simulation version 3.", out.width="100%", fig.asp=1>>= 
@

<<simulations_gdsc_tab3>>=
library(knitr, quietly=TRUE, verbose=FALSE)
suppressWarnings(library(kableExtra))
options(knitr.kable.NA="", digits=3)
kable(tab, col.names=colnames(tab), align="r",
      caption="Median performance measure estimates for simulation version 3 (best performing model in bold).", 
      format="latex", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(latex_options=c("HOLD_position"))
@

@@

	Simulations in Section \ref{sec:simulations} show that the method is 
	reasonably able to recover hyperparameters. In addition, the simulations
	show that inclusion of informative external covariates is indeed beneficial to
	predictive performance. The model is put into practice on the GDSC data. 
	The results in Section
	\ref{sec:gdsc} show that the inclusion of the external covariates is 
	beneficial for drug sensitivity prediction. PMSE of the NIG
	model with both both feature and drug variance components is lower
	than for the regular lasso model and although the PMSE is
	not lower if external covariates are included, the resulting hyperparameter 
	estimates are still informative and may guide future research efforts.
	In addition, the comparison to the bSEM model that allows for the inclusion of 
	one binary external feature covariate favours the proposed NIG model. 
	PMSEs are almost uniformly lower over the drugs for the NIG model 
	compared to bSEM. Consequently, the total PMSE is significantly
	lower for the NIG model.

	A possible direction of future research that attempts 
	to lower PMSE of the NIG model is the introduction of a cross-validated global
	variance component in the prior of the $\bm{\beta}_d$. If we add the 
	additional constraint that the drug and feature variance components have to 
	average to one, this cross-validated variance component may be interpreted as
	the overall level of shrinkage that is then tailored to lower PMSE.

>>>>

	\subsection{Results}
<<simulation_gdsc_res1>>=
res <- read.table("results/simulations_gdsc_res1.txt", row.names=NULL)
temp <- res[, 1]
res <- as.matrix(res[, -1])
rownames(res) <- temp
true.phi <- mean(1/(c(1, 1, 3, 7) %*% t(unname(model.matrix(~ factor(1:4))))))
est.phi <- median(1/res[rownames(res)=="alphaf0", 1])
est.lambdaf <- apply(res[rownames(res)=="lambdaf", c(1, 2)], 2, median)

tab <- cbind(apply(res[rownames(res)=="emsel", ], 2, median),
             apply(res[rownames(res)=="emseh", ], 2, median),
             apply(res[rownames(res)=="emse", ], 2, median),
             apply(res[rownames(res)=="pmse", ], 2, median))
tab <- round(tab, 3)
tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1] <- 
  paste0("\\textbf{", tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1], "}")
tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2] <- 
  paste0("\\textbf{", tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2], "}")
tab[which(tab[, 3]==min(tab[, 3], na.rm=TRUE)), 3] <- 
  paste0("\\textbf{", tab[which(tab[, 3]==min(tab[, 3], na.rm=TRUE)), 3], "}")
tab[which(tab[, 4]==min(tab[, 4], na.rm=TRUE)), 4] <- 
  paste0("\\textbf{", tab[which(tab[, 4]==min(tab[, 4], na.rm=TRUE)), 4], "}")
colnames(tab) <- c("$\\text{EMSE}_{\\text{bottom}}$",
                   "$\\text{EMSE}_{\\text{top}}$",
                   "$\\text{EMSE}_{\\text{total}}$",
                   "$\\text{PMSE}$")     
rownames(tab)[c(1, 2)] <- c("NIG$_{\\text{f}}^-$",
                            "NIG$_{\\text{f}}$")
@	
  Figure \ref{fig:simulations_gdsc_est1} shows the estimated
	$\bm{\alpha}_{\text{feat}}$ together with its true value for NIG$_{\text{f}}$ 
	in version 1 of the simulation study. Figure 
	\ref{fig:simulations_gdsc_est1}a shows that 
	$\bm{\alpha}_{\text{feat}}$ is slightly but 
	consistently underestimated. On the $\phi_{jd}$ scale this underestimation is
	almost undetectable as depicted in Figure
	\ref{fig:simulations_gdsc_est1}b. $\lambda_{\text{feat}}$ is slightly 
	overestimated with median estimate \Sexpr{round(est.lambdaf[2], 2)} (the
	true value is 1). The overestimated $\lambda_{\text{feat}}$ translates 
	into underestimated $\gamma_{jd}^2$ variances. Underestimation of variances is 
	a common phenomenon in variational Bayes approximations. In addition, 
	$\lambda_{\text{feat}}$ is a higher level scale
	parameter, which are, in general, hard to estimate. 
<<simulations_gdsc_est1, fig.cap="Estimated (a) hyperparameters $\\bm{\\alpha}_{\\text{feat}}$ and (b) prior means $\\bm{\\phi}_{jd}$ from simulation version 1 with fixed $\\tau_d^2$.", out.width="100%", fig.asp=1/2>>= 
@

@@

	Table \ref{tab:simulations_gdsc_tab1} displays median estimation MSE 
	(EMSE) and prediction MSE (PMSE) for simulation version 1, calculated on an 
	independent test data set. EMSE is further split into the contribution of the
	bottom 90\% of the $\beta_{jd}$ in terms of size (in absolute value) and the 
	top 10\% of the $\beta_{jd}$ in size. The table includes as a reference the 
	null model, which is an empty model that only fits the means of the $\y_{d}$.
	Estimation MSE (EMSE) and prediction MSE (PMSE) give measures of predictive 
	performance. Focussing on MSE, we see that the NIG$_{\text{f}}$ model, 
	that includes the external covariates, performs best, both in terms of 
	estimation and prediction. The lower MSEs confirm that the model that
	includes the external data (NIG$_{\text{f}}$) learns the underlying structure 
	in the data better than model NIG$_{\text{f}}^-$ that does not include the
	external data. Furthermore, we see that estimation of the larger $\beta_{jd}$ 
	is where ridge loses the most compared to the NIG and lasso models.
<<simulations_gdsc_tab1>>=
library(knitr, quietly=TRUE, verbose=FALSE)
suppressWarnings(library(kableExtra))
options(knitr.kable.NA="", digits=3)
kable(tab, col.names=colnames(tab), align="r",
      caption="Median performance measure for simulation version 1, estimated on the test data (lowest in bold).", 
      format="latex", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(latex_options=c("HOLD_position"))
@

<<simulation_gdsc_res2>>=
res <- read.table("results/simulations_gdsc_res2.txt", row.names=NULL)
temp <- res[, 1]
res <- as.matrix(res[, -1])
rownames(res) <- temp
true.chi <- mean(1/(c(1, 1, 3, 7) %*% t(unname(model.matrix(~ factor(1:4))))))
est.chi <- median(1/res[rownames(res)=="alphad0", 1])
est.lambdad <- apply(res[rownames(res)=="lambdad", c(1, 2)], 2, median)
tab <- cbind(apply(res[rownames(res)=="emsel", ], 2, median),
             apply(res[rownames(res)=="emseh", ], 2, median),
             apply(res[rownames(res)=="emse", ], 2, median),
             apply(res[rownames(res)=="pmse", ], 2, median))
tab <- round(tab, 3)
tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1] <- 
  paste0("\\textbf{", tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1], "}")
tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2] <- 
  paste0("\\textbf{", tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2], "}")
tab[which(tab[, 3]==min(tab[, 3], na.rm=TRUE)), 3] <- 
  paste0("\\textbf{", tab[which(tab[, 3]==min(tab[, 3], na.rm=TRUE)), 3], "}")
tab[which(tab[, 4]==min(tab[, 4], na.rm=TRUE)), 4] <- 
  paste0("\\textbf{", tab[which(tab[, 4]==min(tab[, 4], na.rm=TRUE)), 4], "}")
colnames(tab) <- c("$\\text{EMSE}_{\\text{bottom}}$",
                   "$\\text{EMSE}_{\\text{top}}$",
                   "$\\text{EMSE}_{\\text{total}}$",
                   "$\\text{PMSE}$")      
rownames(tab)[c(1, 2)] <- c("NIG$_{\\text{d}}^-$",
                            "NIG$_{\\text{d}}$")
@	
  Figure \ref{fig:simulations_gdsc_est2} shows the estimated
	$\bm{\alpha}_{\text{drug}}$ together with its true value for NIG$_{\text{d}}$ 
	in version 2 of the simulation study. They are estimated without bias.
	Median $\lambda_{\text{drug}}=\Sexpr{round(est.lambdad[2], 2)}$ is slightly 
	overestimated compared to true value 1. 
	The median $\chi$ estimate in the NIG$_{\text{d}}^-$ model is 
	\Sexpr{round(est.chi, 2)},  
	which is almost equal to the true mean \Sexpr{round(true.chi, 2)}. 
	$\lambda_{\text{drug}}$ is underestimated with median estimate
	\Sexpr{round(est.lambdad[1], 2)} compared to the true value.
	Median performance measures for simulation version 2 are displayed in Table
	\ref{tab:simulations_gdsc_tab2}. Again, we see that NIG$_{\text{d}}$ performs
	best in terms of MSE. However, NIG$_{\text{d}}^-$ performance is the same 
	here, indicating that the external covariates do not add much here.
<<simulations_gdsc_est2, fig.cap="Estimated (a) hyperparameters $\\bm{\\alpha}_{\\text{feat}}$ and (b) prior means $\\bm{\\phi}_{jd}$ from simulation version 2 with fixed $\\gamma_{jd}^2$.", out.width="100%", fig.asp=1/2>>= 
@

<<simulations_gdsc_tab2>>=
library(knitr, quietly=TRUE, verbose=FALSE)
suppressWarnings(library(kableExtra))
options(knitr.kable.NA="", digits=3)
kable(tab, col.names=colnames(tab), align="r",
      caption="Median performance measure for simulation version 2, estimated on the test data (lowest in bold).", 
      format="latex", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(latex_options=c("HOLD_position"))
@

@@

phi.ratio <- apply(apply(sapply(0:3, function(s) {
  res[rownames(res)==paste0("alphaf" ,s), 2]}) %*% 
    t(cbind(1, rbind(0, diag(3)))), 2, function(m) {
      res[rownames(res)=="alphaf0", 2]/m}), 2, median)
chi.ratio <- apply(apply(sapply(0:3, function(s) {
  res[rownames(res)==paste0("alphad" ,s), 2]}) %*% 
    t(cbind(1, rbind(0, diag(3)))), 2, function(m) {
      res[rownames(res)=="alphad0", 2]/m}), 2, median)
true.ratio <- as.numeric(1/(c(1, 1, 3, 7) %*% 
                              t(unname(model.matrix(~ factor(1:4))))))

tab <- cbind(apply(res[rownames(res)=="emsel", ], 2, median),
             apply(res[rownames(res)=="emseh", ], 2, median),
             apply(res[rownames(res)=="emse", ], 2, median),
             apply(res[rownames(res)=="pmse", ], 2, median))
tab <- round(tab, 3)
tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1] <- 
  paste0("\\textbf{", tab[which(tab[, 1]==min(tab[, 1], na.rm=TRUE)), 1], "}")
tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2] <- 
  paste0("\\textbf{", tab[which(tab[, 2]==min(tab[, 2], na.rm=TRUE)), 2], "}")
tab[which(tab[, 3]==min(tab[, 3], na.rm=TRUE)), 3] <- 
  paste0("\\textbf{", tab[which(tab[, 3]==min(tab[, 3], na.rm=TRUE)), 3], "}")
tab[which(tab[, 4]==min(tab[, 4], na.rm=TRUE)), 4] <- 
  paste0("\\textbf{", tab[which(tab[, 4]==min(tab[, 4], na.rm=TRUE)), 4], "}")
colnames(tab) <- c("$\\text{EMSE}_{\\text{bottom}}$",
                   "$\\text{EMSE}_{\\text{top}}$",
                   "$\\text{EMSE}_{\\text{total}}$",
                   "$\\text{PMSE}$")     
rownames(tab)[c(1, 2)] <- c("NIG$_{\\text{f}+\\text{d}}^-$",
                            "NIG$_{\\text{f}+\\text{d}}$")
@	
  In Figure \ref{fig:simulations_gdsc_est3} the 
	$\bm{\alpha}_{\text{feat}}$ and $\bm{\alpha}_{\text{drug}}$ estimated by 
	NIG$_{\text{f}+\text{d}}$
	are displayed together with their true values for
	simulation 3. $\bm{\alpha}_{\text{feat}}$ are underestimated, while 
	$\bm{\alpha}_{\text{drug}}$ are overestimated. These biases seem to 
	be consistent though. The median ratios $\phi_1$ to $\phi_2$, $\phi_3$, 
	$\phi_4$ and $\chi_1$ to $\chi_2$, $\chi_3$, 
	$\chi_4$ are \Sexpr{round(phi.ratio, 2)[-1]} and 
	\Sexpr{round(chi.ratio, 2)[-1]}, respectively, compared to their true values
	\Sexpr{round(true.ratio, 2)[-1]}. So in a relative sense, the estimates are
	correct. Median $\lambda_{\text{feat}}$ and $\lambda_{\text{drug}}$ are
	are over- and underestimated with \Sexpr{round(est.lambdaf[2], 2)}
	and \Sexpr{round(est.lambdad[2], 2)}, respectively, compared to their true
	value 1. The NIG$_{\text{f}+\text{d}}^-$ model is also consistently over- 
	and underestimating $\phi$
	and $\chi$ with estimates \Sexpr{round(est.phi, 2)} and 
	\Sexpr{round(est.chi, 2)}, respectively (compared to the true mean 
	\Sexpr{round(true.chi, 2)}). NIG$_{\text{f}+\text{d}}^-$ also over- and
	underestimates 
	$\lambda_{\text{feat}}$ and $\lambda_{\text{drug}}$ with median estimates
	\Sexpr{round(est.lambdaf[1], 2)}
	and \Sexpr{round(est.lambdad[1], 2)}, respectively. Table 
	\ref{tab:simulations_gdsc_tab3}, with median performance measures, shows
	that NIG$_{\text{f}+\text{d}}$ outperforms the other models in terms of
	prediction and estimation MSE.
<<simulations_gdsc_est3, fig.cap="Estimated (a) hyperparameters $\\bm{\\alpha}_{\\text{feat}}$ and (b) prior means $\\bm{\\phi}_{jd}$ from simulation version 3.", out.width="100%", fig.asp=1>>= 
@

<<simulations_gdsc_tab3>>=
library(knitr, quietly=TRUE, verbose=FALSE)
suppressWarnings(library(kableExtra))
options(knitr.kable.NA="", digits=3)
kable(tab, col.names=colnames(tab), align="r",
      caption="Median performance measure for simulation version 3, estimated on the test data (lowest in bold).", 
      format="latex", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(latex_options=c("HOLD_position"))
@

@@

	Simulations in Section \ref{sec:simulations} show that the method is 
	reasonably able to recover hyperparameters. Simulation versions 1 and 2 show
	that estimation of drug- and feature-specific hyperparameters is, in 
	principle, fairly accurate. However, when estimated jointly, biases may occur
	due to the interplay between the two sources of information. Nevertheless,
	the simulations show that inclusion of informative external covariates is 
	still beneficial to predictive performance.

	The model is put into practice on the GDSC data. 
	The NIG model is competitive with convential models like lasso and ridge.
	We note that estimation of the penalty parameters in the latter two models
	is geared towards predictive performance, because cross-validation is used
	to train these parameters, as opposed to estimation of the
	hyperparameters in the NIG model, which aims to improve model fit. In that 
	sense, the comparison metric (PMSE) is not to the benefit of the NIG model.

	The results in Section
	\ref{sec:gdsc} show that the inclusion of the external covariates covariates 
	indeed substantially modifies the hyperparameters. Although, PMSE of the NIG
	model is not necessarily lower if external covariates are included, the
	resulting hyperparameter 
	estimates are still informative and may guide future research efforts.

	In addition, the comparison to bSEM, a Bayesian counterpart model that allows
	for the inclusion of one binary external feature covariate favours the 
	proposed NIG model. PMSEs are almost uniformly lower over the drugs for the 
	NIG model compared to bSEM. Consequently, the total PMSE is significantly
	lower for the NIG model.

	A possible direction of future research that attempts 
	to lower PMSE of the NIG model is the introduction of a cross-validated global
	variance component in the prior of the $\bm{\beta}_d$. If we add the 
	additional constraint that the drug and feature variance components
	average to one, this cross-validated variance component may be interpreted as
	the overall level of shrinkage. This overall shrinkage level is then tailored 
	to lower PMSE. Other directions of future research are applications of the NIG
	model to different data types. An example of such an application is eQTL, 
	where gene expressions are regressed on SNPs. Several interesting external
	covariates are available, both on the genes as well as the SNPs. An example of
	an external
	covariate for the genes is genelength, where we suspect that longer genes are
	harder to predict. The distance of the SNP to the gene is an example of an
	external SNP covariate, where the expectation is that SNPs further from the 
	gene are less predictive of that gene's expression.
